### 2023-10-17 2.State/lstm.tex
Full lstm
Bew figgures + updates

\section{\acs{LSTM}}\label{sec:lstm}
\acp{LSTM} are a type of \ac{RNN} used to analyze sequence of data. They are capable of predict data based of the previous results. \acp{LSTM} are part of \acp{RNN}. \acp{RNN} are different than feedfoward \acl{NN} because of their feedback connections. Meaning that the results from the last time step have an impact on the next time step.

@@

\begin{figure}[H]
  \centering
  \begin{minipage}{\columnwidth}
    \subfloat[\acs{LSTM} cell\label{fig:lstmCell}]{\includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}}
  \end{minipage}
  \begin{minipage}{\columnwidth}
    \subfloat[Legend\label{leg:lstm}]{\includesvg[width=\textwidth,pretex=\large]{lstm/lstmLegend.svg}}
  \end{minipage}
  \caption{}
\end{figure}

>>>>

\section{\acs{LSTM}}\label{sec:lstm}
\acfp{LSTM} are a type of \ac{RNN} used to analyze sequence of data. They are capable of predict data based of the previous results. \acp{LSTM} are part of \acp{RNN}. \acp{RNN} are different than feedfoward \acl{NN} because of their feedback connections. Meaning that the results from the last time step have an impact on the next time step.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}
  \label{fig:lstmCell}
  \caption{\acs{LSTM} cell}
\end{figure}
